---
title: "sdshw4"
output: html_document
date: "2024-02-19"
---

```{r setup, include=FALSE, results='asis'}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, results='hide'}
library(mosaic)
library(tidyverse)
```

# *Problem 1*

```{r echo=FALSE, results='hide'}
gasprices_data <- read.csv("/Users/disharaj/Downloads/gasprices.csv")
```

# **Claim A : Gas stations charge more if they lack direct competition in sight.**

*Evidence : * 
```{r echo=FALSE}
boot_price_competitors = do(10000)*diffmean(Price ~ Competitors,
data=resample(gasprices_data))
confint(boot_price_competitors, level = 0.95)
```
*Conclusion : *The confidence interval above contains 0 in the interval, which tells us the results are not statistically significant at the 5% level. Thus, we can say that the claim that gas prices tend to increase with no competition cannot be concluded. 

# **CLaim B : The richer the area, the higher the gas prices.**

*Evidence : *
```{r echo=FALSE}
median_income <- median(gasprices_data$Income)
gasprices_data <- gasprices_data %>%
  mutate(High_Income = ifelse(Income > median_income, "Yes", "No"))
boot_price_income = do(10000) * diffmean(Price ~ High_Income,
data=resample(gasprices_data))
confint(boot_price_income, level = 0.95)
```

*Confidence : * The confidence interval above contains 0 in the interval, which tells us the results are not statistically significant at the 5% level. Thus, we can say that the claim that gas prices tend to increase with how richer the are is cannot be concluded. 

# **Claim C : Gas stations at stoplights charge more.**

*Evidence : *
```{r echo=FALSE}
boot_price_stoplight = do(10000) * diffmean(Price ~ Stoplight,
data=resample(gasprices_data))
confint(boot_price_stoplight, level = 0.95)
```
*Conclusion : * The confidence interval above contains 0 in the interval, which tells us the results are not statistically significant at the 5% level. Thus, we can say that the claim that gas prices tend to increase with the presence of a stoplight cannot be concluded. 

# **Claim D : Gas stations with direct highway access charge more.**

*Evidence : * 
```{r echo=FALSE}
boot_price_highway = do(10000) * diffmean(Price ~ Highway,
data=resample(gasprices_data))
confint(boot_price_highway, level = 0.95)
```

*Conclusion : * Since the confidence interval does not contain 0 in the interval, we can say that the results are statistically significant. Thus, we can say that the claim that the price of gas increasing with a presence of a direct highway access can be concluded. 

# **Claim E : Shell charges more than all other non-Shell brands.**

*Evidence : *
```{r echo = FALSE}
gasprices_data <- gasprices_data %>%
  mutate(Shell_Brand = ifelse(Brand %in% c("Shell", "SHELL"), "Shell", "Non-Shell"))
boot_price_shell = do(10000) * diffmean(Price ~ Shell_Brand,
data=resample(gasprices_data))
confint(boot_price_shell, level = 0.95)
```

*Conclusion : * Since the confidence interval does not contain 0 in the interval, we can say that the results are statistically significant. Thus, we can say that the claim that the price of gas differs on the basis of whether the brand is shell or not cannot be concluded.

# *Problem 2*

```{r echo=FALSE, results='hide'}
sclass_data <- read.csv("/Users/disharaj/Downloads/sclass.csv")
```

# **Part A**

```{r echo=FALSE}
sclass_data1 <-sclass_data %>%
   filter(year == 2011 & trim == "63 AMG")
boot_sclass = do(10000) * mean(mileage ~ isOneOwner,
data=resample(sclass_data1))
confint(boot_sclass, level = 0.95)
```
The confidence interval for the average mileage of the the 2011 s - class 63 AMGs hitting the used car market is (25608.50,24575.61).

# **Part B**

```{r echo=FALSE}
sclass_data1 <-sclass_data %>%
   filter(year == 2014 & trim == "550")
sclass_data1 <- sclass_data1 %>%
  mutate(isBlack = color == "Black")
boot_sclass1 = do(10000)*prop(~isBlack,
data=resample(sclass_data1))
confint(boot_sclass1, level = 0.95)
```
The confidence interval for the proportion of 2014 s-class 550s that were painted black is (0.4167532, 0.4527518).

# *Problem 3*

```{r echo=FALSE, results='hide'}
nbc_data <- read.csv("/Users/disharaj/Downloads/nbc_pilotsurvey.csv")
```

# **Part A**
```{r echo=FALSE}
nbc_data1 <- nbc_data %>%
  filter(Show == "Living with Ed" | Show == "My Name is Earl")
boot_nbc = do(10000)*diffmean(Q1_Happy ~ Show,
data=resample(nbc_data1))
confint(boot_nbc, level = 0.95)
```
1) Question: Is there evidence that one show consistently produces a higher mean Q1_Happy response among viewers?
2) Approach:  We use bootstrapping to help us the difference in the means and build a confidence interval. 
3) Results: The 95% confidence interval for the q1_happy parameter for the two shows is (-0.39559, 0.1040292).
4) Conclusion: Since the confidence interval does not contain 0, we can say the result is not statistically significant. Thus, we do not have evidence that one show consistently produces a higher mean Q1_Happy response among viewers.


# **Part B**

```{r echo=FALSE}
nbc_data2 <- nbc_data %>%
  filter(Show == "The Biggest Loser" | Show == "The Apprentice: Los Angeles")
boot_nbc1 = do(10000)*diffmean(Q1_Annoyed ~ Show,
data=resample(nbc_data2))
confint(boot_nbc1, level = 0.95)
```

1) Question: Is there evidence that one show consistently produces a higher mean Q1_Annoyed response among viewers?
2) Approach: We use bootstrapping to help us the difference in the means and build a confidence interval. 
3) Results: The 95% confidence interval for the q1_Annoyed parameter for the two shows is (-0.5240385	, -0.02164403). 
4) Conclusion: Since the confidence interval does not contain 0, we can say the result is statistically significant. Thus, we do have evidence to conclude that one show consistently produces a higher mean Q1_Annoyed response among viewers.

# **Part C**

```{r echo=FALSE}
nbc_data3 <- nbc_data %>%
  filter(Show == "Dancing with the Stars" )
nbc_data3 <- nbc_data3 %>%
  mutate(isHighRating = Q2_Confusing >= 4)
boot_nbc2 = do(10000)*prop(~isHighRating,
data=resample(nbc_data3))
confint(boot_nbc2, level = 0.95)
```
1) Question:  Is there evidence that one show consistently produces a higher mean Q1_Annoyed response among viewers?
2) Approach: We use bootstrapping to help us the difference in the proportions and build a confidence interval.
3) Results: The 95% confidence interval for the proportion of for a response of 4 or greater for the proportion of Americans who found the show confusing is (0.03867403, 0.121547).
4) Conclusion: Since the results are statistically significant, we can say that there is evidence that a significant proportion found the show to be confusing.

# *Problem 4*

```{r echo=FALSE, results='hide'}
ebay_data <- read.csv("/Users/disharaj/Downloads/ebay.csv")
```

```{r echo=FALSE}
ebay_data <- ebay_data %>%
  mutate(rev_ratio = rev_after / rev_before)
boot_ebay = do(10000)*diffmean(rev_ratio~adwords_pause,
data=resample(ebay_data))
confint(boot_ebay, level = 0.95)
```
1) Question: Assess the evidence for whether the revenue ratio is the same in the treatment and control groups, or whether instead the data favors the idea that paid search advertising on Google creates extra revenue for EBay.
2) Approach: We use bootstrapping to help us the difference in the means and build a confidence interval.
3) Results: The 95% confidence interval for the difference in revenue ratio between the treatment and control DMAs is 
(-0.09020481, -0.01273564). 
4) Conclusion: Since 0 is not in the interval, the results are statistically significant. Thus, we can infer that the revenue ratio is systematically higher for the control group, where there was advertising. This could mean that paid search advertising on Google creates extra Revenue for eBay.